Trifunctional Diacylglycerol

### 2025-09-04 LipidProbe/8-3_FattyAcid.qmd
Spent a long time learning about custom divs, applied a new one for cell types
ok one last change, made the sph, 8-3 FA  and dag pages show a line about developing the PSM data visualization, and added collapsible panels

---
title: "Trifunctional 8-3 Fatty Acid"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

::::{.callout-tip}
### Cell background: Huh7

@@

::::{.callout-tip}
### Cell background: HeLa

@@

>>>>

---
title: "Trifunctional 8-3 Fatty Acid"
format: 
  html:
    embed-resources: false
---

@@

::::{.callout-warning collapse="false"}
### Cell background: Huh7

@@

::::{.callout-warning collapse="false"}
### Cell background: HeLa

@@

**\*PSM data presentation still in development.**

See [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) for results in context with Diacylglycerol and 8-3 Fatty Acid data.

### 2025-09-04 LipidProbe/Diacylglycerol.qmd
updating with includes structure
Spent all day learning how to make my heatmap look less bad
trying to distinguish cell types more effectively on individual probe pages
adding credit to Berit for the structures
polishing dag page a little
example
Spent a long time learning about custom divs, applied a new one for cell types
ok one last change, made the sph, 8-3 FA  and dag pages show a line about developing the PSM data visualization, and added collapsible panels

---
title: "Trifunctional Diacylglycerol"
---

@@

## Subcellular localization

@@

>>>>

---
title: "Trifunctional Diacylglycerol"
format: 
  html:
    embed-resources: false
---

@@

:::{.border}
![(A) Trifunctional Diacylglycerol. Preliminary structure collected from Höglinger et al. 2017](/LipidProbe/Structures/TF_DAG.png)
:::

@@

::::{.callout-tip}

### Cell background: HeLa

::: {.callout-note collapse="true"}

{{< include /StudyInformation_includes/DH_2017_include.qmd >}}

:::

**\*PSM data presentation still in development.**

See [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) for results in context with Diacylglycerol and 8-3 Fatty Acid data.

::::
